### 2011-01-26 paper/learningMethods.tex
Few edits

If we choose a value for the five dimensional parameter
$\vec{\theta}$, then a given physical trial gives us one measurement
of the fitness of that parameter vector, or $f(\vec{\theta})$.  Two
things make learnign difficult.  First, each evaluation of
$f(\vec{\theta})$ is expensive, taking 15-20 seconds of time on
average.  Second, the fitness returned by such evaluations has proven
to be very noisy, with the standard deviation of the noise often being
roughly equivalent to the size of the measurement.

@@

In this context, by learning algorithm we simply mean a method for
choosing:

1) The value for $\vec{\theta}$ for the initial trial, and

2) The next value of $\vec{\theta}$ to try, given the $\vec{\theta}$
and $f(\vec{\theta})$ for all previous trials

We evaluated a total of eight subtly or not so subtly different
learning methods.  All employed a simple random sampling method for
requirement (1); that is, all methods picked their initial
$\vec{\theta}$ value via uniform random sampling within the allowed
parameter ranges. \edit{make sure this is true}.  Thus, the
differences in the algorithms was how the selected new $\vec{\theta}$
values to try from their past experience.

>>>>

If we choose a value for the five dimensional parameter
$\vec{\theta}$, then a given physical trial gives us one measurement
of the fitness of that parameter vector, or $f(\vec{\theta})$.  Two
things make learning difficult.  First, each evaluation of
$f(\vec{\theta})$ is expensive, taking 15-20 seconds of time on
average.  Second, the fitness returned by such evaluations has proved
to be very noisy, with the standard deviation of the noise often being
roughly equivalent to the size of the measurement.

@@

In this context, by learning algorithm we mean a method for choosing:

\begin{enumerate}
\item The value for $\vec{\theta}$ for the initial trial, and
\item The next value of $\vec{\theta}$ to try, given the
  $\vec{\theta}$ and $f(\vec{\theta})$ for all previous trials.
\end{enumerate}

We evaluated a total of eight subtly or not so subtly different
learning methods.  All employed a simple random sampling method for
requirement (1); that is, all methods picked their initial
$\vec{\theta}$ value via uniform random sampling within the allowed
parameter ranges. \edit{make sure this is true. Isn't really, should say that we started with A, B, C}.  Thus, the
differences in the algorithms was how they selected new $\vec{\theta}$
values to try from their past experience.
